---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# paralleltrends

<!-- badges: start -->
[![R-CMD-check](https://github.com/audreyrenson/paralleltrends/workflows/R-CMD-check/badge.svg)](https://github.com/audreyrenson/paralleltrends/actions)
<!-- badges: end -->

This package implements the estimators described in the paper titled 'Identifying and estimating effects of sustained treatments under parallel trends assumptions', along with a small simulation (also described in that paper) to illustrate approximate large-sample properties of the estimators, code and data for the application to COVID-19 stay-at-home orders.

## Installation

You can install the development version of paralleltrends from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("audreyrenson/paralleltrends")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(paralleltrends)
## basic example code
```
